### 2019-04-11 paper/paper.tex

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subfig}
\usepackage{listings}
\lstset{numbers=left,stepnumber=1,basicstyle=\footnotesize\ttfamily}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    \def\code#1{\texttt{#1}}
\begin{document}

@@

\author{\IEEEauthorblockN{Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
\IEEEauthorblockA{\textit{Department of Computing Science} \\
\textit{University of Alberta}\\
Edmonton, Canada\\
Email: \{kdehaan,neagu,rsauveho,abram.hindle\}@ualberta.ca}
}

@@

\subsection{Package Metadata}

\begin{lstlisting}[caption={A mock \code{npm} package.json. Some fields omitted for brevity.},captionpos=b,
  label=samplePkg, frame=single, firstline=1]
{
  "name": "Lorem Ipsum",
  "version": "0.9.3",
  "maintainers": [
      {"name": "Dolor Sit",
      "email": "dolorsit@amet.org"}
  ],
  "repository": {
      "type": "git",
      "url": "https://github.com/lor/em"
  },
  "main" : "loremipsum.js",
  "keywords": ["Web", "REST"],
  "dependencies": {
      "Adipiscing": "~1.7.0",
      "Elit": "5.1.x"
  },
  "devDependencies": {
      "Sed": "0.9.0",
      "Do": ">=1.3.5 <4.0.0" 
  }
}
\end{lstlisting}

\textbf{this one is probably mostly for @Fred}

@@

@@

@@

  \bibitem{Wittern:2016}
  Erik Wittern, Philippe Suter, and Shriram Rajagopalan.
  \newblock A look at the dynamics of the javascript package ecosystem.
  \newblock In {\em Proceedings of the 13th International Conference on Mining
    Software Repositories}, MSR '16, pages 351--361, New York, NY, USA, 2016.
    ACM.
  \end{thebibliography}

>>>>

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subfig}
\usepackage{listings}
\usepackage{url}
\lstset{numbers=left,stepnumber=1,basicstyle=\footnotesize\ttfamily}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\def\code#1{\texttt{#1}}
\begin{document}

@@

\author{\IEEEauthorblockN{Kevin de Haan, Frederic Sauve-Hoover, Gregory Neagu, Abram Hindle}
  \IEEEauthorblockA{\textit{Department of Computing Science} \\
    \textit{University of Alberta}\\
    Edmonton, Canada\\
  Email: \{kdehaan,neagu,rsauveho,abram.hindle\}@ualberta.ca}
}

@@

\subsection{Package Metadata} \label{Package Metadata}

\begin{lstlisting}[caption={A mock \code{npm} package.json. Some fields omitted for brevity.},captionpos=b,
  label=samplePkg, frame=single, firstline=1]
{
  "name": "Lorem Ipsum",
  "version": "0.9.3",
  "maintainers": [
      {
        "name": "Dolor Sit",
        "email": "dolorsit@amet.org"
      }
  ],
  "repository": {
      "type": "git",
      "url": "https://github.com/lor/em"
  },
  "main" : "loremipsum.js",
  "keywords": ["Web", "REST"],
  "dependencies": {
      "Adipiscing": "~1.7.0",
      "Elit": "5.1.x"
  },
  "devDependencies": {
      "Sed": "0.9.0",
      "Do": ">=1.3.5 <4.0.0" 
  }
}
\end{lstlisting}

\begin{lstlisting}[caption={A mock simplified \code{npm} metadata file.},captionpos=b,
  label=sampleSimpleMetadata, frame=single, firstline=1][t]
{
  "name": "Lorem Ipsum",
  "versions": {
    "1.0.4": {
      "dependencies": {
        "Adipiscing": "~1.7.0",
        "Elit": "5.1.x"
      },
      "devDependencies": {
        "Sed": "0.9.0",
        "Do": ">=1.3.5 <4.0.0"
      }
    },
    "1.0.5": {
      "dependencies": {
        "Adipiscing": "~1.7.0",
      },
      "devDependencies": {
        "Do": ">=1.3.5 <4.0.0"
      }
    },
    "time": {
      "1.0.4": "2017-09-25T06:39:20.596Z",
      "1.0.5": "2018-05-22T08:35:40.227Z",
      "created": "2015-05-18T03:52:55.192Z"
    }
  }
}
\end{lstlisting}

  Metadata for every package is available on the \code{npm} registry\footnote{https://registry.npmjs.org/packageName}. 
  This metadata is a JSON file containing some info on licensing, documentation links, maintainers, and crucially for 
  our purposes a log of each version of the package since it's creation, labelled using semantic versioning \cite{preston-werner},
  and a time field containing the timestamp for each version. Each version in the version field contains various bits of 
  version specific information such as authors, maintainers, license used, bugs, and a list of dependencies for that specific
  version.\\

  We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{\url{https://skimdb.npmjs.com/registry/_all_docs}}, and then %TODO fix this footnote, underscores are cursed
  downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the npm registry skimdb
  , which we then converted to a somewhat simplified form as in Listing \ref{sampleSimpleMetadata} with just version and dependency information as this is all
  we care about for this study. There are two kinds of dependencies in the metadata files, a list of runtime dependencies and $devDependencies$ used in testing and development.\\

  We gathered some information on download counts for \code{npm} packages from the npmjs API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
  however we found that the npmjs API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
  historic download counts for \code{npm} as a whole or any specific packages.\\

@@

  \begin{figure}
    % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
    \begin{tabular}{c|c|c|c}
      Year & Top 10 & Top 100 & Top 250 \\
      \hline
      2010 & 13 & 103 & 253\\
      2011 & 25 & 297 & 701\\
      2012 & 6 & 46 & 136\\
      2013 & 3 & 38 & 114\\
      2014 & 1 & 40 & 96\\
      2015 & 4 & 38 & 86\\
      2016 & 4 & 29 & 62\\
      2017 & 0 & 12 & 48\\
      2018 & 0 & 15 & 31\\
      2019 & 0 & 4 & 12\\
    \end{tabular}
    \caption{Number of packages entering top \code{npm} ranks for the first time}
    \label{numEnteringTop}
  \end{figure}

@@

  As in the original paper we analyzed popularity of \code{npm} packages using three major measures
  \begin{enumerate}
    \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
      package metadata as described in Section \ref{Package Metadata}. PageRank is calculated for every package using a damping factor of 0.85 
      and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
      \code{npm} rank, an relative ranking of packge popularity with 1 being the most popular.
    \item \textbf{download rank}
  \end{enumerate}

@@

    \bibitem{Wittern:2016}
    Erik Wittern, Philippe Suter, and Shriram Rajagopalan.
    \newblock A look at the dynamics of the javascript package ecosystem.
    \newblock In {\em Proceedings of the 13th International Conference on Mining
    Software Repositories}, MSR '16, pages 351--361, New York, NY, USA, 2016.
    ACM.

    \bibitem{brin1998anatomy}
    Sergey Brin and Lawrence Page.
    \newblock The anatomy of a large-scale hypertextual web search engine.
    \newblock {\em Computer networks and ISDN systems}, 30(1-7):107--117, 1998.

    \bibitem{preston-werner}
    Tom Preston-Werner.
    \newblock Semantic versioning 2.0.0.

\end{thebibliography}
